The Hyperedge Event Model

### 2018-05-30 paper/ba-HEM/ba-sample.tex
typo & citation issue fixed

\address[addr1]{Department of Statistics, Pennsylvania State University
    \printead{e1} % print email address of "e1"
}
\address[addr2]{College of Information and Computer Sciences, UMass Amherst
	\printead{e2} % print email address of "e1"
}
\address[addr3]{Department of Political Science, Pennsylvania State University
	\printead{e3} % print email address of "e1"
}
\address[addr4]{ Microsoft Research NYC
    \printead{e3}
}

@@

We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern time-stamped event formation: 1) the formation of the vertices that are incident to the hyperedge, and 2) the timing of the event in which the edge manifests. In what follows, we introduce the HEM by defining a generative process for time and hyperedge attributed event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference and present tests of our software implementation (Section \ref{sec:inference}). After defining the structure of and deriving Bayesian inference methods for HEM, we demonstrate the model's applicability by analyzing data from a corpus of internal county government emails.  In the application we illustrate model selection, posterior predictive checks, and exploratory analysis (Section \ref{subsec:Emails}). Finally, the paper finishes in Section \ref{sec:conclusion} with conclusion and discussion.

@@

 	   \section{Application to Email Data}\label{subsec:Emails}

>>>>

\address[addr1]{Department of Statistics, Pennsylvania State University
    \printead{e1} % print email address of "e1"
}
\address[addr2]{College of Information and Computer Sciences, UMass Amherst
	\printead{e2} % print email address of "e1"
}
\address[addr3]{Department of Political Science, Pennsylvania State University
	\printead{e3} % print email address of "e1"
}
\address[addr4]{ Microsoft Research NYC
    \printead{e4}
}

@@

We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern time-stamped event formation: 1) the formation of the vertices that are incident to the hyperedge, and 2) the timing of the event in which the edge manifests. In what follows, we introduce the HEM by defining a generative process for time and hyperedge attributed event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference and present tests of our software implementation (Section \ref{sec:inference}). After defining the structure of and deriving Bayesian inference methods for HEM, we demonstrate the model's applicability by analyzing data from a corpus of internal county government emails.  In the application we illustrate model selection, posterior predictive checks, and exploratory analysis (Section \ref{sec:Emails}). Finally, the paper finishes in Section \ref{sec:conclusion} with conclusion and discussion.

@@

 	   \section{Application to Email Data}\label{sec:Emails}
